Beliefs about the development of mental life

### 2021-08-01 supplement/supplement-main.Rmd
fix typos in refs, final table

```{r tabcapcomp, include = T, warning = F, message = F}
d_cap_comp %>%
  select(-Domain) %>%
  mutate(`Study 1` = case_when(`Study 2` != "-" ~ paste0(`Study 1`, 
                                                         footnote_marker_symbol(1)),
                               TRUE ~ `Study 1`)) %>%
  mutate(`Study 1` = case_when(`Study 3` != "-" ~ paste0(`Study 1`, 
                                                         footnote_marker_symbol(2)),
                               TRUE ~ `Study 1`)) %>%
  select(-`Study 2`, -`Study 3`) %>%
  mutate_at(vars(`Gray et al. (2007)`),
            funs(gsub("\\..*", "", .))) %>%
  kable("latex", booktabs = T, escape = F, longtable = T) %>%
  kable_styling(latex_options = c("repeat_header", "striped"), font_size = 8) %>%
  add_header_above(c("Current studies" = 1,
                     "Previous studies" = 5)) %>%
  column_spec(1, width = "4cm") %>%
  column_spec(2:6, width = "2cm") %>%
  pack_rows(group_label = "Bodily sensations", start_row = 1, end_row = 11) %>%
  pack_rows("Negative affect", 12, 16) %>%
  pack_rows("Social connection", 17, 38) %>%
  pack_rows("Cognition and control", 39, 60) %>%
  pack_rows("Not included", 61, nrow(d_cap_comp)) %>%
  footnote(symbol = c("Also used in Study 2; ", "Also unsed in Study 3"),
           symbol_title = "Notes: ",
           footnote_as_chunk = T)
```

>>>>

```{r tabcapcomp, include = T, warning = F, message = F}
d_cap_comp %>%
  select(-Domain) %>%
  mutate_all(~gsub("similar to .", "similar to \\`", .)) %>% 
  mutate(`Study 1` = case_when(`Study 2` != "-" ~ paste0(`Study 1`, 
                                                         footnote_marker_symbol(1)),
                               TRUE ~ `Study 1`)) %>%
  mutate(`Study 1` = case_when(`Study 3` != "-" ~ paste0(`Study 1`, 
                                                         footnote_marker_symbol(2)),
                               TRUE ~ `Study 1`)) %>%
  select(-`Study 2`, -`Study 3`) %>%
  mutate_at(vars(`Gray et al. (2007)`),
            funs(gsub("\\..*", "", .))) %>%
  kable("latex", booktabs = T, escape = F, longtable = T) %>%
  kable_styling(latex_options = c("repeat_header", "striped"), font_size = 8) %>%
  add_header_above(c("Current studies" = 1,
                     "Previous studies" = 5)) %>%
  column_spec(1, width = "4cm") %>%
  column_spec(2:6, width = "2cm") %>%
  pack_rows(group_label = "Bodily sensations", start_row = 1, end_row = 11) %>%
  pack_rows("Negative affect", 12, 16) %>%
  pack_rows("Social connection", 17, 38) %>%
  pack_rows("Cognition and control", 39, 60) %>%
  pack_rows("Not included", 61, nrow(d_cap_comp)) %>%
  footnote(symbol = c("Also used in Study 2; ", "Also used in Study 3"),
           symbol_title = "Notes: ",
           footnote_as_chunk = T)
```
